Arrows for Parallel Computation

### 2018-01-21 paper/content/futures.tex
wip

\section{Futures} \label{sec:futures}\label{futures}
\begin{figure}[t]
\begin{code}
someCombinator:: (ArrowChoice arr,
	ArrowParallel arr a b (),
	ArrowParallel arr b c ()) =>
	[arr a b] -> [arr b c] -> arr [a] [c]
someCombinator fs1 fs2 =
	parEvalN () fs1 >>>
	rightRotate >>>
	parEvalN () fs2
\end{code}
\caption{The outline combinator.}
\label{fig:someCombinator}
\end{figure}

>>>>

\section{Futures} \label{sec:futures}\label{futures}
\begin{figure}[t]
\begin{code}
someCombinator :: (ArrowChoice arr,
	ArrowParallel arr a b (),
	ArrowParallel arr b c ()) =>
	[arr a b] -> [arr b c] -> arr [a] [c]
someCombinator fs1 fs2 =
	parEvalN () fs1 >>>
	rightRotate >>>
	parEvalN () fs2
\end{code}
\caption{The outline combinator.}
\label{fig:someCombinator}
\end{figure}
